### 2022-10-28 draft/draft.Rmd
modified drosophila example to use all four labels

In the final example, we examined the *Drosophila* connectome graph \citep{Eichler141762}, which has been studied as a GRDPG by \citet{athreya2017statistical}, \citet{https://doi.org/10.48550/arxiv.1705.03297}, and \citet{SannaPassino2022}. 
In this graph, each vertex is a neuron, and the labels correspond to one of four neuron types (Kenyon Cells, Input Neurons, Output Neurons, and Projection Neurons). 
In our analysis, we only considered neurons labeled as Kenyon Cells and Projection Neurons in the right hemisphere. 
The resulting graph is illustrated in figure \ref{fig:mbconnectome-graph}.

The ASE in two dimensions suggest that the MBM with one dimensional quadratic manifolds is an appropriate model for this graph (figure \ref{fig:mbconnectome-ase}). 
Fitting two quadratic Bezier curves to the ASE (figure \ref{fig:mbconnectome-kcurves}) results in 91.4\% accuracy.

```{r mbconnectome-graph, fig.cap = 'Drosophila connectome graph. Each vertex represents a neuron, which are labeled by neuron type.', fig.height = 2, figh.width = 4}
library(mbstructure)
data(MBconnectome)

graph <- generate.graph(newrdat, vdf.right)
A <- as.matrix(igraph::as_adjacency_matrix(graph$g, type = 'both'))
z <- graph$vdf$type
ind.keep <- z %in% c('KC', 'PN')
A <- A[ind.keep, ind.keep]
z <- as.numeric(as.factor(as.numeric(z[ind.keep])))
A <- sign(A + t(A))
diag(A) <- 0

```{r mbconnectome-ase, fig.cap = 'ASE of the Drosophila connectome graph. The embedding vectors are labeled by neuron type.', fig.height = 2, fig.width = 8}
Xhat <- embedding(A, 2, 0)

ggplot() + 
  geom_point(aes(x = Xhat[, 1], y = Xhat[, 2],
                 colour = factor(z))) + 
  coord_fixed(.5) +
  theme_bw() + 
  theme(legend.position = 'none') +
  scale_colour_brewer(palette = 'Set1') + 
  labs(x = expression(x[1]), y = expression(x[2]),
       colour = NULL)
```

```{r mbconnectome-kcurves, fig.cap = 'ASE of the Drosophila connectome graph with quadratic Bezier curves fitted via $K$-curves clustering. The embedding vectors are colored by predicted label.', fig.height = 2, fig.width = 8, cache = TRUE}
set.seed(314159)
z.init <- sample.points(z, 3)

mbconnectome.out <- manifold.clustering(Xhat, 2, 
                                        initialization = z.init,
                                        intercept = FALSE, 
                                        parallel = TRUE, 
                                        verbose = FALSE, 
                                        animate = FALSE, 
                                        curve.init = 'x')

plot.estimated.curves(Xhat, mbconnectome.out) + 
  scale_colour_brewer(palette = 'Set1') + 
  coord_fixed(.4) +
  labs(x = expression(x[1]), y = expression(x[2]))
```

>>>>

In the final example, we examined the *Drosophila* connectome graphs \citep{Eichler141762}, which has been studied as a GRDPG by \citet{athreya2017statistical}, \citet{https://doi.org/10.48550/arxiv.1705.03297}, and \citet{SannaPassino2022}. 
This dataset consists of two graphs representing two networks of neurons, one for each hemisphere of the *Drosophila* brain. 
In these graphs, each vertex is a neuron, and the labels correspond to one of four neuron types (Kenyon Cells, Input Neurons, Output Neurons, and Projection Neurons). 
The resulting graphs are illustrated in figure \ref{fig:mbconnectome-graph}.

The ASE in two dimensions suggest that the MBM with one dimensional quadratic manifolds is an appropriate model for these graphs (figure \ref{fig:mbconnectome-ase}). 
Fitting two quadratic Bezier curves to the ASEs (figure \ref{fig:mbconnectome-kcurves}) results in 69.9\% accuracy for the left hemisphere connectome and 76.5\% accuracy for the right hemisphere connectome.

```{r mbconnectome-graph, fig.cap = 'Graphs of the Drosophila connectomes. The left and right are of the left and right hemispheres, respectively. Each vertex represents a neuron, which are labeled by neuron type.', fig.height = 2, figh.width = 12}
library(mbstructure)
data(MBconnectome)

graph.r <- generate.graph(newrdat, vdf.right)
A.r <- as.matrix(igraph::as_adjacency_matrix(graph.r$g, type = 'both'))
z.r <- as.numeric(graph.r$vdf$type)
n.r <- length(z.r)
A.r <- sign(A.r + t(A.r))
diag(A.r) <- 0
graph.r <- ggraph(A.r, layout = 'stress') + 
  geom_edge_link(alpha = 1 / sqrt(n.r) / 2) + 
  geom_node_point(aes(colour = factor(z.r)), 
                  show.legend = FALSE) + 
  labs(colour = NULL) + 
  theme_void() + 
  scale_colour_brewer(palette = 'Set1')

graph.l <- generate.graph(newldat, vdf.left)
A.l <- as.matrix(igraph::as_adjacency_matrix(graph.l$g, type = 'both'))
z.l <- as.numeric(graph.l$vdf$type)
n.l <- length(z.l)
Al <- sign(A.l + t(A.l))
diag(A.l) <- 0
graph.l <- ggraph(A.l, layout = 'stress') + 
  geom_edge_link(alpha = 1 / sqrt(n.l) / 2) + 
  geom_node_point(aes(colour = factor(z.l)), 
                  show.legend = FALSE) + 
  labs(colour = NULL) + 
  theme_void() + 
  scale_colour_brewer(palette = 'Set1')

gridExtra::grid.arrange(graph.l, graph.r, nrow = 1)
```

```{r mbconnectome-ase, fig.cap = 'ASE of the Drosophila connectome graphs. The embedding vectors are labeled by neuron type.', fig.height = 2, fig.width = 12}
Xhat.l <- embedding(A.l, 2, 0)
ase.l <- ggplot() + 
  geom_point(aes(x = Xhat.l[, 1], y = Xhat.l[, 2],
                 colour = factor(z.l))) + 
  coord_fixed(.5) +
  theme_bw() + 
  theme(legend.position = 'none') +
  scale_colour_brewer(palette = 'Set1') + 
  labs(x = NULL, y = NULL, colour = NULL)

Xhat.r <- embedding(A.r, 2, 0)
ase.r <- ggplot() + 
  geom_point(aes(x = Xhat.r[, 1], y = Xhat.r[, 2],
                 colour = factor(z.r))) + 
  coord_fixed(.5) +
  theme_bw() + 
  theme(legend.position = 'none') +
  scale_colour_brewer(palette = 'Set1') + 
  labs(x = NULL, y = NULL, colour = NULL)

gridExtra::grid.arrange(ase.l, ase.r, nrow = 1)
```

```{r mbconnectome-kcurves, fig.cap = 'ASEs of the Drosophila connectome graphs with quadratic Bezier curves fitted via $K$-curves clustering. The embedding vectors are colored by predicted label.', fig.height = 2, fig.width = 12, cache = TRUE}
set.seed(314159265)

z.init.r <- sample.points(z.r, 10)
z.init.l <- sample.points(z.l, 10)

mbconnectome.out.r <- manifold.clustering(Xhat.r, 
                                          length(unique(z.r)), 
                                          initialization = z.init.r,
                                          intercept = FALSE, 
                                          parallel = TRUE, 
                                          verbose = FALSE, 
                                          animate = FALSE, 
                                          curve.init = 'x')
fitted.r <- plot.estimated.curves(Xhat.r, mbconnectome.out.r) + 
  scale_colour_brewer(palette = 'Set1') + 
  coord_fixed(.4) +
  labs(x = NULL, y = NULL)

mbconnectome.out.l <- manifold.clustering(Xhat.l, 
                                          length(unique(z.l)), 
                                          initialization = z.init.l,
                                          intercept = FALSE, 
                                          parallel = TRUE, 
                                          verbose = FALSE, 
                                          animate = FALSE, 
                                          curve.init = 'x')
fitted.l <- plot.estimated.curves(Xhat.l, mbconnectome.out.l) + 
  scale_colour_brewer(palette = 'Set1') + 
  coord_fixed(.4) +
  labs(x = NULL, y = NULL)

gridExtra::grid.arrange(fitted.l, fitted.r, nrow = 1)
```

### 2022-10-28 draft/draft.tex
modified drosophila example to use all four labels

In the final example, we examined the \emph{Drosophila} connectome graph \citep{Eichler141762}, which has been studied as a GRDPG by \citet{athreya2017statistical}, \citet{https://doi.org/10.48550/arxiv.1705.03297}, and \citet{SannaPassino2022}.
In this graph, each vertex is a neuron, and the labels correspond to one of four neuron types (Kenyon Cells, Input Neurons, Output Neurons, and Projection Neurons).
In our analysis, we only considered neurons labeled as Kenyon Cells and Projection Neurons in the right hemisphere.
The resulting graph is illustrated in figure \ref{fig:mbconnectome-graph}.

The ASE in two dimensions suggest that the MBM with one dimensional quadratic manifolds is an appropriate model for this graph (figure \ref{fig:mbconnectome-ase}).
Fitting two quadratic Bezier curves to the ASE (figure \ref{fig:mbconnectome-kcurves}) results in 91.4\% accuracy.

@@

\caption{Drosophila connectome graph. Each vertex represents a neuron, which are labeled by neuron type.}\label{fig:mbconnectome-graph}
\end{figure}

@@

\caption{ASE of the Drosophila connectome graph. The embedding vectors are labeled by neuron type.}\label{fig:mbconnectome-ase}
\end{figure}

@@

\caption{ASE of the Drosophila connectome graph with quadratic Bezier curves fitted via $K$-curves clustering. The embedding vectors are colored by predicted label.}\label{fig:mbconnectome-kcurves}
\end{figure}

>>>>

In the final example, we examined the \emph{Drosophila} connectome graphs \citep{Eichler141762}, which has been studied as a GRDPG by \citet{athreya2017statistical}, \citet{https://doi.org/10.48550/arxiv.1705.03297}, and \citet{SannaPassino2022}.
This dataset consists of two graphs representing two networks of neurons, one for each hemisphere of the \emph{Drosophila} brain.
In these graphs, each vertex is a neuron, and the labels correspond to one of four neuron types (Kenyon Cells, Input Neurons, Output Neurons, and Projection Neurons).
The resulting graphs are illustrated in figure \ref{fig:mbconnectome-graph}.

The ASE in two dimensions suggest that the MBM with one dimensional quadratic manifolds is an appropriate model for these graphs (figure \ref{fig:mbconnectome-ase}).
Fitting two quadratic Bezier curves to the ASEs (figure \ref{fig:mbconnectome-kcurves}) results in 69.9\% accuracy for the left hemisphere connectome and 76.5\% accuracy for the right hemisphere connectome.

@@

\caption{Graphs of the Drosophila connectomes. The left and right are of the left and right hemispheres, respectively. Each vertex represents a neuron, which are labeled by neuron type.}\label{fig:mbconnectome-graph}
\end{figure}

@@

\caption{ASE of the Drosophila connectome graphs. The embedding vectors are labeled by neuron type.}\label{fig:mbconnectome-ase}
\end{figure}

@@

\caption{ASEs of the Drosophila connectome graphs with quadratic Bezier curves fitted via $K$-curves clustering. The embedding vectors are colored by predicted label.}\label{fig:mbconnectome-kcurves}
\end{figure}
